---
title: "Leaflet demo"
author: "J.L. van der Plas"
date: "26 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```

## Leaflet demo

This is a small demonstration of leaflet, a tool for crearting maps in R. We will show a map of the world, with markers that show the name pof the coutry and the popuploation when you click on the marker. 

## Loading the data demo

We combine the population data from the world bank with the longitude / lattidute data from the open suorce project 

```{r load data}
countries <- read.csv("countries.csv", sep=";")
countries_pop <- read.csv("countries_population.csv", sep=",")
countries_complete <- merge(countries, countries_pop, by.x = "cca3", by.y = "CountryCode")
countries_complete$coord = as.character(countries_complete$latlng)
coords_split <- strsplit(countries_complete$coord,split=",")
countries_complete$lat <- as.numeric(unlist(coords_split)[2*(1:nrow(countries_complete))-1])
countries_complete$lng <- as.numeric( unlist(coords_split)[2*(1:nrow(countries_complete))])
countries_complete$popupText <- paste0("<b>Country</b>: ",
                countries_complete$CountryName,
                "<br/>", "<b>Population</b>:",
                as.character(countries_complete$X2016))
```

## Create the map

We create the map using mostly the default options, except we enable clustering of markers 

```{r pressure, echo=FALSE}
mymap <- leaflet(countries_complete) %>% 
  addTiles() %>% 
  addMarkers(~lng, ~lat, popup = ~popupText, clusterOptions = markerClusterOptions())

mymap
```

